Figures

### 2019-05-14 figures/08_exploratory_dotplot.Rmd
remove nlcd and junk predictors

```{r 08_exploratory_dotplot, echo=FALSE, message=TRUE, eval=TRUE}
dt     <- readRDS("../data/dt.rds")
dt_sub <- dplyr::select(dt, tp, tn, lake_area_ha:wheat, -other.non.ag, 
                        -mixed.crop) %>%
  dplyr::filter(complete.cases(.)) %>%
  mutate_all(as.numeric) %>%
  data.frame(stringsAsFactors = FALSE)

>>>>

```{r 08_exploratory_dotplot, echo=FALSE, message=TRUE, eval=TRUE}
dt     <- readRDS("../data/dt.rds")
dt_sub <- dplyr::select(dt, tp, tn, lake_area_ha:wheat, -other.non.ag, 
                        -mixed.crop) %>%
  dplyr::select(-row_crop_pct, -ag_pct, -pasture_pct) %>%
  dplyr::select(-matches("other")) %>%
  dplyr::filter(complete.cases(.)) %>%
  mutate_all(as.numeric) %>%
  data.frame(stringsAsFactors = FALSE)
